---
title: "Professions classification summaries"
author: "Anshu Uppal"
date: "`r lubridate::today()`"
output: 
  html_document:
    code_folding: hide
knit: (function(input, ...) {
    rmarkdown::render(
      input, 
      output_dir = here::here("output")
    )
  })
---

```{r setup, results = "hide", message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)  # Set default to not display code from chunks and not to display warnings
options(width = 300)
# Load packages and dataset ####
pacman::p_load(    # Installs / loads packages if they are not already installed / loaded
  here,       # File locator
  tidyverse,
  flextable
)

# Input dataset
# Read in datasets ####
merged <- readRDS("P:/ODS/DMCPRU/UEPDATA/Specchio-COVID19/99_data/Base_de_données/classification_jobs_anup_jan_2024/2024-02-29-1553_ISCO_fuzzy_recoded_occupations.rds")
merged <- readRDS(here("output", "ISCO_fuzzy_recoded_occupations.rds"))

# Reorder ISCO labels as factors
merged <- merged |> 
  mutate(
    ISCO_label_full = fct_reorder(ISCO_label_full, isco_full),
    ISCO_label_3 = fct_reorder(ISCO_label_3, isco_3),
    ISCO_label_2 = fct_reorder(ISCO_label_2, isco_2),
    ISCO_label_1 = fct_reorder(ISCO_label_1, isco_1),
    # ISCO codes
    # isco_1 = factor(isco_1),
    # isco_2 = factor(isco_2),
    # isco_3 = factor(isco_3),
    # isco_full = factor(isco_full)
  )

# Sante-travail 2022
st_22 <- readRDS("P:/ODS/DMCPRU/UEPDATA/Specchio-COVID19/99_data/Bases_for_sharing/2023-09-21-1145_SanteTravail_ALLparticipants.rds") |> select(participant_id, job_sector)

# Sante-travail 2023
st_23 <- readRDS("P:/ODS/DMCPRU/UEPDATA/Pour_user/Pour_Anshu/santé_travail_11_2023-202401221247.rds")|> # preliminary version from Sergeui
  group_by(participant_id) |> filter(n() < 2) |> ungroup()  # remove duplicate entries

sector_st_23 <- st_23 |> select(participant_id, starts_with("job_sector")) |> 
  select(-job_sector_other_text) |>
  mutate(
    across(
      # job_sector_commerce:job_sector_99,
      starts_with("job_sector"),
      ~na_if(., FALSE)
    ))
wc <- droplevels(col(sector_st_23, as.factor=TRUE)[which(sector_st_23 == "TRUE")])
sector_st_23[levels(wc)] <- Map(factor, sector_st_23[levels(wc)], labels = levels(wc))
sector_st_23 <- sector_st_23 |> 
  unite("job_sector", job_sector_commerce:job_sector_99, na.rm = TRUE, sep = " ; ") |> 
  mutate(job_sector = str_replace_all(job_sector, "job_sector_",""),
         job_sector = str_replace(job_sector, "99","Other")
  )
st_23 <- left_join(st_23, sector_st_23) |> 
  select(participant_id, job_sector)
rm(sector_st_23, wc)


# Define function for flextable
# define standard myflextable function 
myflextable = function(data, ...) {
  set_flextable_defaults(na_str = "NA", theme_fun = theme_booktabs, font.size = 12, padding.bottom = 1, padding.top = 1)
  x = flextable(data, ...)
  x = colformat_int(x, big.mark = "")
  x = colformat_double(x, big.mark = "", 
                       digits = 2,
                       na_str = "NA")
  return(x)
}
```
# Profession summaries {.tabset}
```{r}
# Occupation summaries ####
summary_overall <- merged |> 
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  mutate(ISCO_label = "Overall", ISCO = "-") |> 
  relocate(c(ISCO_label, ISCO), .before = N)

summary_overall_pop <- merged |> 
  filter(serocov_pop | sp2_novdec_2020 | sp3_juin_2021 | sp4_avril_2022) |> 
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  mutate(ISCO_label = "Overall", ISCO = "-") |> 
  relocate(c(ISCO_label, ISCO), .before = N)

# Level 1
summary_level_1 <- merged |> 
  group_by(ISCO_label_1, isco_1) |> 
  # count(ISCO_label_1, isco_1,health_workers)
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  rename(ISCO_label = ISCO_label_1, ISCO = isco_1) |> 
  mutate(ISCO = as.integer(ISCO)) |> 
  arrange(ISCO)

summary_level_1_pop <- merged |> 
  filter(serocov_pop | sp2_novdec_2020 | sp3_juin_2021 | sp4_avril_2022) |> 
  group_by(ISCO_label_1, isco_1) |> 
  # count(ISCO_label_1, isco_1,health_workers)
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  rename(ISCO_label = ISCO_label_1, ISCO = isco_1) |> 
  mutate(ISCO = as.integer(ISCO)) |> 
  arrange(ISCO)

# Level 2
summary_level_2 <- merged |> 
  group_by(ISCO_label_2, isco_2) |> 
  # count(ISCO_label_1, isco_1,health_workers)
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  rename(ISCO_label = ISCO_label_2, ISCO = isco_2) |> 
  mutate(ISCO = as.integer(ISCO)) |> 
  arrange(ISCO)

summary_level_2_pop <- merged |> 
  filter(serocov_pop | sp2_novdec_2020 | sp3_juin_2021 | sp4_avril_2022) |> 
  group_by(ISCO_label_2, isco_2) |> 
  # count(ISCO_label_1, isco_1,health_workers)
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  rename(ISCO_label = ISCO_label_2, ISCO = isco_2) |> 
  mutate(ISCO = as.integer(ISCO)) |> 
  arrange(ISCO)

# Level 3
summary_level_3 <- merged |> 
  group_by(ISCO_label_3, isco_3) |> 
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  rename(ISCO_label = ISCO_label_3, ISCO = isco_3) |> 
  mutate(ISCO = as.integer(ISCO)) |> 
  arrange(ISCO)

summary_level_3_pop <- merged |> 
  filter(serocov_pop | sp2_novdec_2020 | sp3_juin_2021 | sp4_avril_2022) |> 
  group_by(ISCO_label_3, isco_3) |> 
  # count(ISCO_label_1, isco_1,health_workers)
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  rename(ISCO_label = ISCO_label_3, ISCO = isco_3) |> 
  mutate(ISCO = as.integer(ISCO)) |> 
  arrange(ISCO)
```

## ISCO summaries {.tabset}  
Below are a few summaries, where N is the number of participants in each grouping, HCW_n is the number of healthcare workers in each grouping, and HCW_percent is the percentage of healthcare workers in each grouping (= HCW_n  / N). Note: N can include multiple entries for a single participant, if they replied to more than one of the questionnaires considered here (WORK, Inclusion-KIDS, and Santé-Travail 2022/2023).  

NA are those not yet classified, and “Recoding impossible” are people who submitted non-answers, e.g. “---”, or answers that don’t correspond to ISCO classifications, e.g. “étudiant” or “mere au foyer”.  

### ISCO level 1
**By the most general ISCO grouping (“Major groups”)**
```{r}
summary_1 <- rbind(summary_overall, summary_level_1) 
summary_1 |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```

The same as above but keeping only participants recruited from one of the respresentative serosurveys (SP1, SP2, SP3, SP4):
```{r}
summary_1_pop <- rbind(summary_overall_pop, summary_level_1_pop) 
summary_1_pop |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```

### ISCO level 2
**By the level 2 ISCO grouping:**
```{r}
summary_2 <- rbind(summary_overall, summary_level_2) 
summary_2 |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```
The same as above but keeping only participants recruited from one of the respresentative serosurveys (SP1, SP2, SP3, SP4):
```{r}
summary_2_pop <- rbind(summary_overall_pop, summary_level_2_pop) 
summary_2_pop |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```

### ISCO level 3
**By the level 3 ISCO grouping:**
```{r}
summary_3 <- rbind(summary_overall, summary_level_3) 
summary_3 |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```
The same as above but keeping only participants recruited from one of the respresentative serosurveys (SP1, SP2, SP3, SP4):
```{r}
summary_3_pop <- rbind(summary_overall_pop, summary_level_3_pop) 
summary_3_pop |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```

## Job sector summaries {.tabset}
### Harmonized  
**Job sector using the "harmonized" variable:**
We still need to confirm how to define the WORK sectors and also how to define a single job sector for Santé-Travail 2023, where participants could select multiple job sectors.
```{r}
summary_sector_overall <- merged |> 
  summarise(
    N = n(),
    HCW_n = sum(health_workers, na.rm = TRUE),
    HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  mutate(job_sector_harmonized = "Overall") |> 
  relocate(c(job_sector_harmonized), .before = N)

summary_sector <- merged |> 
  group_by(job_sector_harmonized) |> 
  summarise(
    N = n(),
    HCW_n = sum(health_workers, na.rm = TRUE),
    HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  )

sector_summary <- rbind(summary_sector_overall, summary_sector)
sector_summary |> myflextable() |> 
  width(j = 1, 3.8, unit = "in") |> 
  bold(i = 1)
```

### ST 2023 - to check  
These are the responses for job sector from Santé-Travail 2023. When multiple responses were selected, they are separated by a ";".  

For the "harmonized" job sectors, I recoded these three of the multicombinations as follows:  
"health_social ; public_admin" --> "Santé, social, médico-social"  
"legal_accounting ; public_admin" --> "Enseignement, recherche"  
"public_admin ; education_research" --> "Activités juridiques, comptabilité, secrétariat"

I then recoded all of the other multicombinations as "Other".

The numbers in these other multicombinations are relatively low, but still worth some discussion to see how to treat them.
```{r}
# Job sector summaries: st_23 ####
merged_st_23 <- left_join(merged, st_23) |>   filter(!is.na(job_sector) & source == "st_23")
merged_st_23_overall <- merged_st_23 |> 
  summarise(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")
  ) |> 
  mutate(job_sector = "Overall") |> 
  relocate(job_sector, .before = N)

merged_st_23 <- merged_st_23 |> 
  mutate(
    job_sector_lumped = job_sector,
    job_sector_lumped = forcats::fct_lump_min(job_sector_lumped,1,other_level = "Other")
    ) |> 
  group_by(job_sector_lumped) |> 
  summarize(N = n(),
            HCW_n = sum(health_workers, na.rm = TRUE),
            HCW_percent = paste0(round(HCW_n / N, 3)*100, "%")) |> 
  rename(job_sector = job_sector_lumped) |> 
  arrange(-N)

st23_sectors <- rbind(merged_st_23_overall, merged_st_23) 
# c("health_social ; public_admin", "legal_accounting ; public_admin", "public_admin ; education_research")
sec_rows <-which(st23_sectors$job_sector %in% c("health_social ; public_admin", "legal_accounting ; public_admin", "public_admin ; education_research"))
st23_sectors |> 
  myflextable() |> 
  width(j = 1, 4, unit = "in") |> 
  bold(i = sec_rows)
```

## Consistency {.tabset}
### ISCO codes {.tabset}
Check consistency in the ISCO codes when we have data from two timepoints.  

The label in the left column is the profession in the indicated dataset, n_pairs shows the number of instances where that profession has matching data for the same participant data at the other timepoint.

the consistent column shows how many of those pairs of data show identical professions (i.e. profession remained consistent between the two timepoints).

percent shows the percentage of consistent matches.

#### Level 1
```{r}
consistency_1 <- merged |> 
  filter(isco_full != -999) |> 
  group_by(codbar) |> filter(n()>1) |> 
  select(codbar, source, ISCO_label_1) |> 
  pivot_wider(names_from = source,
              values_from = c(ISCO_label_1)) |> 
  mutate(
    st_22_st_23 = case_when(is.na(st_22) | is.na(st_23) ~ NA, st_22 == st_23 ~ TRUE, .default = FALSE),
    st_22_work = case_when(is.na(st_22) | is.na(Work) ~ NA, st_22 == Work ~ TRUE, .default = FALSE),
    st_22_inc_kids = case_when(is.na(st_22) | is.na(inc_kids) ~ NA, st_22 == inc_kids ~ TRUE, .default = FALSE),
    st_23_work = case_when(is.na(st_23) | is.na(Work) ~ NA, st_23 == Work ~ TRUE, .default = FALSE),
    st_23_inc_kids = case_when(is.na(st_23) | is.na(inc_kids) ~ NA, st_23 == inc_kids ~ TRUE, .default = FALSE),
    work_inc_kids = case_when(is.na(Work) | is.na(inc_kids) ~ NA, Work == inc_kids ~ TRUE, .default = FALSE)
    )
```

**Consistency between Santé-Travail 2022 and 2023**
```{r}
consistency_1_st <- consistency_1 |> 
  group_by(st_22) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_st_23)),
    consistent = sum(st_22_st_23, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) |> 
  filter(!is.na(st_22))
consistency_1_st |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

**Consistency between Santé-Travail 2022 and WORK**
```{r}
consistency_1_st22_work <- consistency_1 |> 
  group_by(st_22) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_work)),
    consistent = sum(st_22_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) |> 
  filter(!is.na(st_22))
consistency_1_st22_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

**Consistency between Santé-Travail 2023 and WORK**
```{r}
consistency_1_st23_work <- consistency_1 |> 
  group_by(st_23) |> 
  summarise(
    n_pairs = sum(!is.na(st_23_work)),
    consistent = sum(st_23_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) |> 
  filter(!is.na(st_23))
consistency_1_st23_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

#### Level 2
```{r}
consistency_2 <- merged |> 
  filter(isco_full != -999) |> 
  group_by(codbar) |> filter(n()>1) |> 
  select(codbar, source, ISCO_label_2) |> 
  pivot_wider(names_from = source,
              values_from = ISCO_label_2) |> 
  mutate(
    st_22_st_23 = case_when(is.na(st_22) | is.na(st_23) ~ NA, st_22 == st_23 ~ TRUE, .default = FALSE),
    st_22_work = case_when(is.na(st_22) | is.na(Work) ~ NA, st_22 == Work ~ TRUE, .default = FALSE),
    st_22_inc_kids = case_when(is.na(st_22) | is.na(inc_kids) ~ NA, st_22 == inc_kids ~ TRUE, .default = FALSE),
    st_23_work = case_when(is.na(st_23) | is.na(Work) ~ NA, st_23 == Work ~ TRUE, .default = FALSE),
    st_23_inc_kids = case_when(is.na(st_23) | is.na(inc_kids) ~ NA, st_23 == inc_kids ~ TRUE, .default = FALSE),
    work_inc_kids = case_when(is.na(Work) | is.na(inc_kids) ~ NA, Work == inc_kids ~ TRUE, .default = FALSE)
    )
```

**Consistency between Santé-Travail 2022 and 2023**
```{r}
consistency_2_st <- consistency_2 |> 
  group_by(st_22) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_st_23)),
    consistent = sum(st_22_st_23, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) |> 
  filter(!is.na(st_22))
consistency_2_st |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

**Consistency between Santé-Travail 2022 and WORK**
```{r}
consistency_2_st22_work <- consistency_2 |> 
  group_by(st_22) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_work)),
    consistent = sum(st_22_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) |> 
  filter(!is.na(st_22))
consistency_2_st22_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

**Consistency between Santé-Travail 2023 and WORK**
```{r}
consistency_2_st23_work <- consistency_2 |> 
  group_by(st_23) |> 
  summarise(
    n_pairs = sum(!is.na(st_23_work)),
    consistent = sum(st_23_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) |> 
  filter(!is.na(st_23))
consistency_2_st23_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

#### Level 3
```{r}
consistency_3 <- merged |> 
  filter(isco_full != -999) |> 
  group_by(codbar) |> filter(n()>1) |> 
  select(codbar, source, ISCO_label_3) |> 
  pivot_wider(names_from = source,
              values_from = ISCO_label_3) |> 
  mutate(
    st_22_st_23 = case_when(is.na(st_22) | is.na(st_23) ~ NA, st_22 == st_23 ~ TRUE, .default = FALSE),
    st_22_work = case_when(is.na(st_22) | is.na(Work) ~ NA, st_22 == Work ~ TRUE, .default = FALSE),
    st_22_inc_kids = case_when(is.na(st_22) | is.na(inc_kids) ~ NA, st_22 == inc_kids ~ TRUE, .default = FALSE),
    st_23_work = case_when(is.na(st_23) | is.na(Work) ~ NA, st_23 == Work ~ TRUE, .default = FALSE),
    st_23_inc_kids = case_when(is.na(st_23) | is.na(inc_kids) ~ NA, st_23 == inc_kids ~ TRUE, .default = FALSE),
    work_inc_kids = case_when(is.na(Work) | is.na(inc_kids) ~ NA, Work == inc_kids ~ TRUE, .default = FALSE)
    )
```

**Consistency between Santé-Travail 2022 and 2023**
```{r}
consistency_3_st <- consistency_3 |> 
  group_by(st_22) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_st_23)),
    consistent = sum(st_22_st_23, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) 
consistency_3_st |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

**Consistency between Santé-Travail 2022 and WORK**
```{r}
consistency_3_st22_work <- consistency_3 |> 
  group_by(st_22) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_work)),
    consistent = sum(st_22_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) 
consistency_3_st22_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

**Consistency between Santé-Travail 2023 and WORK**
```{r}
consistency_3_st23_work <- consistency_3 |> 
  group_by(st_23) |> 
  summarise(
    n_pairs = sum(!is.na(st_23_work)),
    consistent = sum(st_23_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) 
consistency_3_st23_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

### Job sectors {.tabset}
Check consistency in job sector when we have data from two timepoints
```{r}
consistency_job_sectors <- merged |> 
  filter(!is.na(job_sector_harmonized)) |> 
  group_by(codbar) |> filter(n()>1) |> 
  select(codbar, source, job_sector_harmonized) |> 
  pivot_wider(names_from = source,
              values_from = job_sector_harmonized) |> 
  ungroup() |> 
  mutate(
    st_22_st_23 = case_when(is.na(st_22) | is.na(st_23) ~ NA, st_22 == st_23 ~ TRUE, .default = FALSE),
    st_22_work = case_when(is.na(st_22) | is.na(Work) ~ NA, st_22 == Work ~ TRUE, .default = FALSE),
    st_23_work = case_when(is.na(st_23) | is.na(Work) ~ NA, st_23 == Work ~ TRUE, .default = FALSE),
    )
```

#### ST 22_23
**Consistency between Santé-Travail 2022 and 2023**
```{r}
consistency_job_sectors_st <- consistency_job_sectors |> 
  group_by(factor(st_22)) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_st_23)),
    consistent = sum(st_22_st_23, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) 
consistency_job_sectors_st |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

#### ST22_Work
**Consistency between Santé-Travail 2022 and WORK**
```{r}
consistency_job_sectors_st22_work <- consistency_job_sectors |> 
  group_by(factor(st_22)) |> 
  summarise(
    n_pairs = sum(!is.na(st_22_work)),
    consistent = sum(st_22_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) 
consistency_job_sectors_st22_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```

#### ST23_Work
**Consistency between Santé-Travail 2023 and WORK**
```{r}
consistency_job_sectors_st23_work <- consistency_job_sectors |> 
  group_by(factor(st_23)) |> 
  summarise(
    n_pairs = sum(!is.na(st_23_work)),
    consistent = sum(st_23_work, na.rm = TRUE),
    percent = paste0(round(consistent / n_pairs, 2)*100, "%")
  ) 
consistency_job_sectors_st23_work |> myflextable() |> 
    width(j = 1, 3.8, unit = "in")
```
